---
title: "R Notebook"
output: html_notebook
---


```{r}

library(dplyr)
library(tidyverse)
library(ggplot2)
library(ggwordcloud)
library(stringr)

```

```{r}
coffee_raw = read.csv('coffee_survey.csv')
```

```{r}
#EDA

summary(coffee_raw)
length(coffee_raw) #57 columns
nrow(coffee_raw) #4042 rows
cat('df shape ',dim(coffee_raw)) #4042
coffee_raw %>% #num NAs
  summarise(across(everything(), ~ sum(is.na(.))))
```


```{r}

#Dropping rows with no information and all who did not participate in the survey. 
coffee_cleaning = coffee_raw %>%
filter(rowSums(is.na(coffee_raw))!=55 & rowSums(is.na(coffee_raw))!=56)
coffee_cleaning = coffee_cleaning %>%
  filter(!is.na(coffee_a_bitterness))
dim(coffee_cleaning) #3798
coffee_cleaning

#Factorizing
coffee_cleaning$cups = as.factor(coffee_cleaning$cups)
coffee_cleaning$age = as.factor(coffee_cleaning$age)
coffee_cleaning$favorite = as.factor(coffee_cleaning$favorite)
coffee_cleaning$style = as.factor(coffee_cleaning$style)
coffee_cleaning$strength = as.factor(coffee_cleaning$strength)
coffee_cleaning$roast_level = as.factor(coffee_cleaning$roast_level)
coffee_cleaning$caffeine = as.factor(coffee_cleaning$caffeine)
coffee_cleaning$prefer_abc = as.factor(coffee_cleaning$prefer_abc)
coffee_cleaning$prefer_overall = as.factor(coffee_cleaning$prefer_overall)
coffee_cleaning$wfh = as.factor(coffee_cleaning$wfh)
coffee_cleaning$total_spend = as.factor(coffee_cleaning$total_spend)
coffee_cleaning$most_paid = as.factor(coffee_cleaning$most_paid)
coffee_cleaning$most_willing = as.factor(coffee_cleaning$most_willing)
coffee_cleaning$value_cafe = as.factor(coffee_cleaning$value_cafe)
coffee_cleaning$spent_equipment = as.factor(coffee_cleaning$spent_equipment)
coffee_cleaning$value_equipment = as.factor(coffee_cleaning$value_equipment)
coffee_cleaning$gender = as.factor(coffee_cleaning$gender)
coffee_cleaning$education_level = as.factor(coffee_cleaning$education_level)
coffee_cleaning$ethnicity_race = as.factor(coffee_cleaning$ethnicity_race)
coffee_cleaning$number_children = as.factor(coffee_cleaning$number_children)


# Feature Engineering, Home and Additions
coffee_cleaning = coffee_cleaning %>% mutate(cafe = if_else(str_detect(where_drink, "cafe"), "Cafe", "No"),
                           go = if_else(str_detect(where_drink, "go"), "On the go", "No"),
                           home = if_else(str_detect(where_drink, "home"), "Home", "No"),
                           office = if_else(str_detect(where_drink, "office"), "Office", "No"),
                           no_place = if_else(str_detect(where_drink, "cafe"), "None", "No"),
                           pour_over = if_else(str_detect(brew, "Pour"), "Pour over", "No"),
                           french_press = if_else(str_detect(brew, "French"), "French press", "No"),
                           espresso = if_else(str_detect(brew, "Espresso"), "Espresso", "No"),
                           brewer = if_else(str_detect(brew, "Mr."), "Drip Brewer", "No"),
                           pod = if_else(str_detect(brew, "Nespresso"), "Pod", "No"),
                           instant = if_else(str_detect(brew, "Instant"), "Instant", "No"),
                           bean_cup = if_else(str_detect(brew, "Bean"), "Bean to Cup Machine", "No"),
                           extract = if_else(str_detect(brew, "Cometeer"), "Extract, like Cometeer", "No"),
                           cold_brew = if_else(str_detect(brew, "Cold"), "Cold brew", "No"),
                           other_brew = if_else(str_detect(brew, "Other"), "Other", "No"),
                           other_loc = if_else(str_detect(purchase, "Other"), "Other", "No"),
                           drive_thru = if_else(str_detect(purchase, "Drive"), "Drive Thru", "No"),
                           local_cafe = if_else(str_detect(purchase, "Local"), "Local cafe", "No"),
                           deli = if_else(str_detect(purchase, "Deli"), "Deli", "No"),
                           specialty = if_else(str_detect(purchase, "Specialty"), "Speciality Cafe", "No"),
                           chain = if_else(str_detect(purchase, "Dunkin"), "Chain", "No"))

coffee_cleaning = coffee_cleaning %>% mutate(coffee_black = if_else(str_detect(additions, "just"), "Black", "Milk/Sugar"))

#Capitalize column names
#coffee_cleaning <- coffee_cleaning %>% rename_with(~ str_to_title(.))
#coffee_cleaning
coffee_cleaning

write.csv(coffee_cleaning, "heh/coffee_cleaning.csv", row.names = FALSE)
```
```{r}
#Regular base r plot for testing
coffee_cleaning %>% 
  ggplot(aes(age)) +
  geom_bar()

```

```{r} 

#PIVOT FOR TESTING

coffee_cleaning %>%
  separate(where_drink, sep=',', fill = 'right', into = c('x1','x2','x3','x4','x5','x6', 'x7','x8','x9','x10'
                                                   ), remove = TRUE) %>%
  pivot_longer(
    cols = x1:x10,
    names_to = 'list',
    values_to = 'x') %>%
  filter(!is.na(x)) %>%
  mutate(x = str_trim(x)) %>%
  #ggplot(aes(x, y = ..count../sum(..count..))) +
  ggplot(aes(x, y = ..count../(sum(!is.na(coffee_cleaning$where_drink))))) +
  geom_bar(aes(fill = wfh)) +
  scale_y_continuous(labels = scales::percent_format()) +
  labs(y = 'Percent Respondents',
       title = '') +
  guides(x = guide_axis(n.dodge=1, angle = 320)) +
  geom_text(aes(label = ..count..), stat = "count", vjust = -.5, colour = "black") +
  annotate("text", x = Inf, y = Inf, label = paste("Total sample size:", sum(!is.na(coffee_cleaning$purchase))), 
           hjust = 1.1, vjust = 2, size = 4, color = "black")

#PIVOT FOR PRODUCTION - don't run here
coffee_cleaning %>%
      separate(!!input$pivotX, sep=',', fill = 'right', into = c('x1','x2','x3','x4','x5','x6', 'x7','x8','x9','x10'
      ), remove = TRUE) %>%
      pivot_longer(
        cols = x1:x10,
        names_to = 'list',
        values_to = 'x') %>%
      filter(!is.na(x)) %>%
      mutate(x = str_trim(x)) %>%
      ggplot(aes(x, y = ..count../(sum(!is.na(coffee_cleaning%>%select(!!input$pivotX)))))) +
      geom_bar(aes(fill = !!input$pivotZ)) +
      scale_y_continuous(labels = scales::percent_format()) +
      labs(y = 'Percent Respondents', x = NULL) +
      guides(x = guide_axis(n.dodge=1, angle = 320)) +
      geom_text(aes(label = ..count..), stat = "count", vjust = -.5, colour = "black") +
      annotate("text", x = Inf, y = Inf, label = paste("Total sample size:", sum(!is.na(coffee_cleaning%>%select(!!input$pivotX)))), 
               hjust = 1.1, vjust = 2, size = 6, color = "black") +
      theme(axis.text.x = element_text(size = 12),
            axis.text.y = element_text(size = 12),
            axis.title.x = element_text(size = 14, face = 'bold'),
            axis.title.y = element_text(size = 14, face = 'bold'))
```

```{r}
library(scales)
scales::percent_format(.44)
percent(.44)

# SIMPLE FOR TESTING

coffee_cleaning %>% 
  ggplot(aes(roast_level,y = ..count../sum(..count..))) +
  geom_bar(aes(fill = favorite)) +
  scale_y_continuous(labels = scales::percent_format()) +
  labs(y = 'Percent Respondents',
       title = 'Comparisons') +
  guides(x = guide_axis(n.dodge=1, angle = 320)) +
  geom_text(aes(label = ..count..), stat = "count", vjust = -.5, colour = "black") +
  annotate("text", x = Inf, y = Inf, label = paste("Total sample size:", sum(!is.na(coffee_cleaning$Age))), 
           hjust = 1.1, vjust = 2, size = 4, color = "black")


#SIMPLE FOR PRODUCTION - don't run

output$simple_plot <- renderPlot({
    coffee_cleaning %>% 
      ggplot(aes(!!input$simpleX, y = ..count../sum(..count..))) +
      geom_bar(aes(fill = !!input$simpleZ)) +
      scale_y_continuous(labels = scales::percent_format()) +
      labs(y = 'Percent Respondents', x = NULL) + 
      guides(x = guide_axis(n.dodge=1, angle = 320)) +
      geom_text(aes(label = ..count..), stat = "count", vjust = -.5, colour = "black") +
      annotate("text", x = Inf, y = Inf, label = paste("Total sample size:", sum(!is.na(coffee_cleaning%>%select(!!input$simpleX)))), 
          hjust = 1.1, vjust = 2, size = 6, color = "black") +
      theme(axis.text.x = element_text(size = 12),
            axis.text.y = element_text(size = 12),
            axis.title.x = element_text(size = 14, face = 'bold'),
            axis.title.y = element_text(size = 14, face = 'bold'))
```
```{r}

#RESULT DETAILS PAGE PRODUCTION

#DF IN GLOBAL.R
results = coffee_cleaning %>%
  pivot_longer(cols = c(coffee_a_acidity, coffee_a_bitterness, coffee_a_personal_preference,
                        coffee_b_acidity, coffee_b_bitterness, coffee_b_personal_preference,
                        coffee_c_acidity, coffee_c_bitterness, coffee_c_personal_preference,
                        coffee_d_acidity, coffee_d_bitterness, coffee_d_personal_preference),
               values_to = 'score',
               names_to = 'metric') %>%
  mutate(type = case_when(
    str_detect(metric, "coffee_a") ~ "A",
    str_detect(metric, "coffee_b") ~ "B",
    str_detect(metric, "coffee_c") ~ "C",
    str_detect(metric, "coffee_d") ~ "D",
  ))

# FOR APP.R               
results %>%
  filter(type == 'A') %>%
  ggplot() +
  geom_density(aes(score, color = metric), binwidth = 1, adjust = 4) +
  scale_y_continuous(labels = scales::percent_format()) +
  labs(y = 'Percent Respondents',
       title = 'Tasting Scores') +
  #guides(x = guide_axis(n.dodge=1, angle = 320)) +
  annotate("text", x = Inf, y = Inf, label = paste("Total sample size:", #sum(!is.na(coffee_dropped$Age))), 
           nrow(results %>%
  filter((type == 'A') & (str_detect(metric, "acidity"))) %>%
  group_by(submission_id) %>%
  summarise(n()))),
           hjust = 1.1, vjust = 2, size = 4, color = "black")


```

```{r}

#WORK CLOUD FOR TESTING

#Making a smaller DF
master_word_cloud = rbind(
  
coffee_cleaning %>%
  select(submission_id, coffee_a_notes) %>%
  filter(!is.na(coffee_a_notes)) %>%
  mutate(coffee_a_notes = str_replace_all(coffee_a_notes, "[<>.*]", " ")) %>%
  separate_wider_delim(col = coffee_a_notes, delim = " ",
                       names = c("var1", "var2", "var3", "var4", "var5", "var6", "var7", "var8", "var9", "var10", "var11", "var12", "var13", "var14", "var15", "var16"),  
                       too_many = "debug",
                       too_few = "debug") %>%
  pivot_longer(cols = starts_with('var'),
               names_to = 'place',
               values_to = 'words', 
               values_drop_na = TRUE) %>%
  mutate(words = str_trim(words)) %>%
  mutate(words = str_replace(words, ",", "")) %>%
  mutate(words = tolower(words)) %>%
  count(words, name = 'count') %>%
  filter((count > 5) & (count < 100)) %>%
  filter(words %in% c("as","a", "i", "4", "3rd", "bit", "and", "it", "b", "<ul>", "&","-") == FALSE) %>%
  mutate(Type = 'A'),

#B Word Clooud
coffee_cleaning %>%
  select(submission_id, coffee_b_notes) %>%
  filter(!is.na(coffee_b_notes)) %>%
  mutate(coffee_b_notes = str_replace_all(coffee_b_notes, "[<>.*]", " ")) %>%
  separate_wider_delim(col = coffee_b_notes, delim = " ",
                       names = c("var1", "var2", "var3", "var4", "var5", "var6", "var7", "var8", "var9", "var10", "var11", "var12", "var13", "var14", "var15", "var16"),  
                       too_many = "debug",
                       too_few = "debug") %>%
  pivot_longer(cols = starts_with('var'),
               names_to = 'place',
               values_to = 'words', 
               values_drop_na = TRUE) %>%
  mutate(words = str_trim(words)) %>%
  mutate(words = str_replace(words, ",", "")) %>%
  mutate(words = tolower(words)) %>%
  count(words, name = 'count') %>%
  filter((count > 5) & (count < 100)) %>%
  filter(words %in% c("as","a", "i", "4", "3rd", "bit", "and", "it", "b", "<ul>", "&","-") == FALSE) %>%
  mutate(Type = 'B'),

#C word cloud
coffee_cleaning %>%
  select(submission_id, coffee_c_notes) %>%
  filter(!is.na(coffee_c_notes)) %>%
  mutate(coffee_c_notes = str_replace_all(coffee_c_notes, "[<>.*]", " ")) %>%
  separate_wider_delim(col = coffee_c_notes, delim = " ",
                       names = c("var1", "var2", "var3", "var4", "var5", "var6", "var7", "var8", "var9", "var10", "var11", "var12", "var13", "var14", "var15", "var16"),  
                       too_many = "debug",
                       too_few = "debug") %>%
  pivot_longer(cols = starts_with('var'),
               names_to = 'place',
               values_to = 'words', 
               values_drop_na = TRUE) %>%
  mutate(words = str_trim(words)) %>%
  mutate(words = str_replace(words, ",", "")) %>%
  mutate(words = tolower(words)) %>%
  count(words, name = 'count') %>%
  filter((count > 5) & (count < 100)) %>%
  filter(words %in% c("as","a", "i", "4", "3rd", "bit", "and", "it", "b", "<ul>", "&","-") == FALSE) %>%
  mutate(Type = 'C'),

#D wordcloud
coffee_cleaning %>%
  select(submission_id, coffee_d_notes) %>%
  filter(!is.na(coffee_d_notes)) %>%
  mutate(coffee_d_notes = str_replace_all(coffee_d_notes, "[<>.*]", " ")) %>%
  separate_wider_delim(col = coffee_d_notes, delim = " ",
                       names = c("var1", "var2", "var3", "var4", "var5", "var6", "var7", "var8", "var9", "var10", "var11", "var12", "var13", "var14", "var15", "var16"),  
                       too_many = "debug",
                       too_few = "debug") %>%
  pivot_longer(cols = starts_with('var'),
               names_to = 'place',
               values_to = 'words', 
               values_drop_na = TRUE) %>%
  mutate(words = str_trim(words)) %>%
  mutate(words = str_replace(words, ",", "")) %>%
  mutate(words = tolower(words)) %>%
  count(words, name = 'count') %>%
  filter((count > 5) & (count < 100)) %>%
  filter(words %in% c("as","a", "i", "4", "3rd", "bit", "and", "it", "b", "<ul>", "&","-") == FALSE) %>%
  mutate(Type = 'D')
)

write.csv(master_word_cloud, "heh/master_word_cloud.csv", row.names = FALSE)

master_word_cloud %>%
      filter(Type == 'B') %>%
      ggplot(aes(label = words, size = count, color = count)) +
      geom_text_wordcloud_area(rm_outside = TRUE, eccentricity = 1) +
      scale_size_area(max_size = 50, trans = power_trans(1/.7)) +
      theme_minimal() +
      scale_color_gradient(low = "darkred", high = "red")
      

  
```

```{r}
#HEAD TO HEAD SCORE

coffee_cleaning %>%
  pivot_longer( cols = ends_with('preference'),
                values_to = 'Scores',
                names_to = 'Coffee_choice') %>%
  ggplot(aes(x = Coffee_choice)) +
  stat_summary(aes(y = Scores, fill = caffeine), 
               position = 'dodge', na.rm = TRUE, fun = "mean", geom = "bar") + 
  scale_x_discrete(labels = c("coffee_a_personal_preference" = "Coffee A", 
                              "coffee_b_personal_preference" = "Coffee B", 
                              "coffee_c_personal_preference" = "Coffee C",
                              "coffee_d_personal_preference" = "Coffee D")) +
  theme(axis.text.x = element_text(size = 12),
        axis.text.y = element_text(size = 12),
        axis.title.x = element_text(size = 14, face = 'bold'),
        axis.title.y = element_text(size = 14, face = 'bold'))
  
```

```{r}

#PREFER ABC

coffee_cleaning %>%
  ggplot(aes(prefer_abc,y = ..count../sum(..count..))) +
  geom_bar(aes(fill = age), position = 'stack') +
  scale_y_continuous(labels = scales::percent_format()) +
  labs(y = 'Percent Respondents', x = NULL) + 
  geom_text(aes(label = ..count..), stat = "count", vjust = -.5, colour = "black") +
  annotate("text", x = Inf, y = Inf, label = paste("Total sample size:", 3798), 
          hjust = 1.1, vjust = 2, size = 6, color = "black") + 
  theme(axis.text.x = element_text(size = 12),
        axis.text.y = element_text(size = 12),
        axis.title.x = element_text(size = 14, face = 'bold'),
        axis.title.y = element_text(size = 14, face = 'bold'))
```

```{r}
#PREFER A OR D

coffee_cleaning %>%
  ggplot(aes(prefer_ad, y = ..count../sum(..count..))) +
  geom_bar(aes(fill = age), position = 'stack') +
  scale_y_continuous(labels = scales::percent_format()) +
  labs(y = 'Percent Respondents', x = NULL) + 
  geom_text(aes(label = ..count..), stat = "count", vjust = -.5, colour = "black") +
  annotate("text", x = Inf, y = Inf, label = paste("Total sample size:", 3798), 
          hjust = 1.1, vjust = 2, size = 6, color = "black") + 
  theme(axis.text.x = element_text(size = 12),
        axis.text.y = element_text(size = 12),
        axis.title.x = element_text(size = 14, face = 'bold'),
        axis.title.y = element_text(size = 14, face = 'bold'))
```
```{r}

#PREFER OVERALL

coffee_cleaning %>%
  ggplot(aes(prefer_overall, y = ..count../sum(..count..))) +
  geom_bar(aes(fill = age), position = 'stack') +
  scale_y_continuous(labels = scales::percent_format()) +
  labs(y = 'Percent Respondents', x = NULL) + 
  geom_text(aes(label = ..count..), stat = "count", vjust = -.5, colour = "black") +
  annotate("text", x = Inf, y = Inf, label = paste("Total sample size:", 3798), 
          hjust = 1.1, vjust = 2, size = 6, color = "black") + 
  theme(axis.text.x = element_text(size = 12),
        axis.text.y = element_text(size = 12),
        axis.title.x = element_text(size = 14, face = 'bold'),
        axis.title.y = element_text(size = 14, face = 'bold'))

```

```{r}
 #SUMMARY SCORES

coffee_cleaning %>%
  pivot_longer( cols = c(ends_with('bitterness'), ends_with('preference')),
                values_to = 'Scores',
                names_to = 'Coffee_choice') %>%
  mutate(Type = if_else(str_detect(Coffee_choice, "_a"), "A",
                if_else(str_detect(Coffee_choice, "_b"), "B",
                if_else(str_detect(Coffee_choice, "_c"), "C",
                if_else(str_detect(Coffee_choice, "_d"), "D", "E"))))) %>%
  filter(Type == 'A') %>%
  select(Scores)

as.data.frame(summary(coffee_cleaning %>%
  select(contains(paste0('_',tolower(st),'_'))))) %>%
  select(Var2,Freq) %>%
  rename(Characteristic = Var2) %>%
  filter(str_detect(Freq,'Mean'))
  
  pivot_wider(names_from = Var2,
              values_from = Freq
              )
  

st = 'A'
tolower(st)
paste0('_',tolower(st),'_')
```
```{r}

#SEGMENTER
coffee_cleaning %>%
  #filter((!is.na(age)) & (!is.na(favorite))) %>%
  ggplot(aes(age, gender)) +
  stat_summary_2d(aes(z = coffee_a_personal_preference), fun = 'mean', bins = 30) +
  geom_count() +
  scale_fill_viridis_c() +
  guides(x = guide_axis(n.dodge=1, angle = 320))


#MEANS
coffee_cleaning %>%
  select(ends_with('preference')) %>%
  summarise(Coffee_A = mean(coffee_a_personal_preference, na.rm = TRUE),
            Coffee_B = mean(coffee_b_personal_preference, na.rm = TRUE),
            Coffee_C = mean(coffee_c_personal_preference, na.rm = TRUE),
            Coffee_D = mean(coffee_d_personal_preference, na.rm = TRUE)
            )
            
            
            
            
```
```{r}

#SEGMENT + PIVOT
coffee_cleaning %>%
  separate(age, sep=',', fill = 'right', into = c('x1','x2','x3','x4','x5','x6', 'x7','x8','x9','x10'
                                                   ), remove = TRUE) %>%
  pivot_longer(
    cols = x1:x10,
    names_to = 'list',
    values_to = 'x') %>%
  filter(!is.na(x)) %>%
  mutate(x = str_trim(x)) %>%
  ggplot(aes(x, coffee_black)) +
  stat_summary_2d(aes(z = coffee_a_personal_preference), fun = 'mean', bins = 30) +
  geom_count() +
  scale_fill_viridis_c() +
  guides(x = guide_axis(n.dodge=1, angle = 320))

```

```{r}
#Except NULL for F Test, variances are similiar
var.test(coffee_cleaning$coffee_b_personal_preference, coffee_cleaning$coffee_c_personal_preference, alternative = "two.sided")[3] #p = 0.4149961

t.test(coffee_cleaning$coffee_b_personal_preference, coffee_cleaning$coffee_c_personal_preference, alternative = "two.sided")[3] #p=.9

var.test(coffee_cleaning$coffee_b_acidity, coffee_cleaning$coffee_c_acidity, alternative = "two.sided") [3] #p = 0.0001

t.test(coffee_cleaning$coffee_b_acidity, coffee_cleaning$coffee_c_acidity, alternative = "two.sided")[3] #p=3.87529e-12

var.test(coffee_cleaning$coffee_b_bitterness, coffee_cleaning$coffee_c_bitterness, alternative = "two.sided") [3] #p = 0.7

t.test(coffee_cleaning$coffee_b_bitterness, coffee_cleaning$coffee_c_bitterness, alternative = "two.sided")[3] #p=.009

cor.test(coffee_cleaning$coffee_b_acidity, coffee_cleaning$coffee_b_personal_preference) #p=.015
```
```{r}


mlm = inner_join(inner_join(
coffee_cleaning %>%
  select(submission_id,ends_with('acidity')) %>%
  pivot_longer(cols = ends_with('acidity'), names_to = "type", values_to = "acidity") %>%
  separate(type, c('type') , '_acidity'),
coffee_cleaning %>%
  select(submission_id,ends_with('bitterness')) %>%
  pivot_longer(cols = ends_with('bitterness'), names_to = "type", values_to = "bitterness") %>%
  separate(type, c('type') , '_bitterness'),
by = c("submission_id", 'type')),
coffee_cleaning %>%
  select(submission_id,ends_with('preference')) %>%
  pivot_longer(cols = ends_with('preference'), names_to = "type", values_to = "preference") %>%
  separate(type, c('type') , '_personal_preference'),
by = c("submission_id", 'type')
)

#
mlm %>%
  ggplot(aes(acidity, preference)) +
  geom_density2d_filled(adjust = 2, contour_var = 'count')
  

mlm %>%
  ggplot(aes(bitterness, preference)) +
  geom_density2d_filled(adjust = 2, contour_var = 'count')
  
  
cor.test(mlm$acidity, mlm$preference)
cor.test(mlm$bitterness, mlm$preference)


`````````
```{r}
corr_bit = inner_join(
coffee_cleaning %>%
  select(submission_id,ends_with('bitterness')) %>%
  pivot_longer(cols = ends_with('bitterness'), names_to = "type", values_to = "bitterness") %>%
  separate(type, c('type') , '_bitterness'),
coffee_cleaning %>%
  select(submission_id,ends_with('preference')) %>%
  pivot_longer(cols = ends_with('preference'), names_to = "type", values_to = "preference") %>%
  separate(type, c('type') , '_personal_preference'),
by = c("submission_id", 'type')
)
corr_bit
cor.test(corr_bit$bitterness, corr_bit$preference)


is.na(corr_bit)
```
```{r}
coffee_cleaning %>%
  select(starts_with('coffee') & !ends_with('notes')) %>%
  summarise_all(mean, na.rm = TRUE) %>%
  pivot_longer(cols = everything(), names_to = 'names', values_to = 'values')
    
  )
```
```{r}
#6 oz - 10 grams, 340g
ratio = 10/6*8
ratio
340/ratio
#25 cups of coffee per bag
18/25
```


```{r}
summary(model) #Many predictor variables are not significant, yet the
                         #overall regression is significant.

plot(model) #Assessing the assumptions of the model.

library(car) #Companion to applied regression.
influencePlot(model)

vif(model) #Assessing the variance inflation factors for the variables
                     #in our model.

#Added variable plots for assessing the contribution of each additional variable.
avPlots(model) #Distinct patterns are indications of good contributions
                         
#to the model; absent patterns usually are pointers to
                         #variables that could be dropped from the model.


```

Old Code




```{r}
#Dropping submission that are missing 56 or 55 inputs. 

coffee_dropped = coffee_raw %>%
filter(rowSums(is.na(coffee_raw))!=55 & rowSums(is.na(coffee_raw))!=56)

# Total Participants
dim(coffee_dropped) #4010
cat('participants of survey ', dim(coffee_dropped)[1]) 

# Participants of the tasting
yes_tasting = coffee_dropped %>%
  filter(!is.na(coffee_a_bitterness))
cat('participants of tasting ', dim(yes_tasting)[1]) #3798

# NOT Participants of the tasting
no_tasting = coffee_dropped %>%
  filter(is.na(coffee_a_bitterness))
cat('participants of tasting ', dim(no_tasting)[1]) #244
no_tasting_id = no_tasting$submission_id
no_tasting_id


```
```{r}
coffee_dropped$survey = ifelse(!is.na(coffee_dropped$coffee_a_bitterness), 'tasting was completed', 'tasting NOT completed') 
coffee_dropped$cups = factor(coffee_dropped$cups, levels = c("Less than 1", "1", "2", "3", "4", "More than 4","NA"))
coffee_dropped <- coffee_dropped %>% rename_with(~ str_to_title(.))


coffee_dropped %>% 
  ggplot(aes(age,y = ..count../sum(..count..))) +
  geom_bar(aes(fill = survey)) +
  scale_y_continuous(labels = scales::percent_format()) +
  #geom_bar() +
  labs(y = 'Percent Respondents',
       title = 'Ages of Respondents') +
  guides(x = guide_axis(n.dodge=1, angle = 320)) +
  geom_text(aes(label = ..count..), stat = "count", vjust = -.5, colour = "black") +
  annotate("text", x = Inf, y = Inf, label = paste("Total sample size:", nrow(coffee_dropped)), 
           hjust = 1.1, vjust = 2, size = 4, color = "black")

```
```{r}
plot(coffee_dropped$age)
```

```{r}
coffee_dropped %>% 
  ggplot(aes(age)) +
  geom_bar(aes(fill = survey)) +
  guides(x = guide_axis(n.dodge=1, angle = 320)) +
  geom_text(aes(label = round(..count../sum(..count..),2)), stat = "count", colour = "black") +
  guides(x = guide_axis(n.dodge=1, angle = 320))


```


```{r}
coffee_dropped %>% 
  ggplot(aes(gender, y = ..count../sum(..count..))) +
  geom_bar(aes(fill = age)) +
  scale_y_continuous(labels = scales::percent_format()) +
  geom_text(aes(label = ..count..), stat = "count", vjust = -.5, colour = "black") +
  guides(x = guide_axis(n.dodge=1, angle = 320)) +
  labs(x = "Gender", y = "Percent Respondents", title = "Coffee Cups per Day") +
  annotate("text", x = Inf, y = Inf, label = paste("Total sample size:", nrow(coffee_dropped)), 
           hjust = 1.1, vjust = 2, size = 4, color = "black")

long %>%
  ggplot(aes(gender, y = ..count../sum(..count..))) +
  geom_bar(aes(fill = age)) +
  scale_y_continuous(labels = scales::percent_format()) +
  #geom_text(aes(label = ..count..), stat = "count", vjust = -.5, colour = "black") +
  guides(x = guide_axis(n.dodge=1, angle = 320)) +
  labs(x = "Gender", y = "Percent Respondents", title = "Coffee Cups per Day") #+
  annotate("text", x = Inf, y = Inf, label = paste("Total sample size:", nrow(coffee_dropped)), 
          hjust = 1.1, vjust = 2, size = 4, color = "black")
```
```{r}
coffee_dropped %>%
  #select(submission_id, age, where_drink) %>%
  separate(Where_drink, sep=',', fill = 'right', into = c('where1','where2','where3','where4','where5','where6'
                                                   ), remove = TRUE) %>%
  pivot_longer(
    cols = where1:where6,
    names_to = 'list',
    values_to = 'brew_where') %>%
  select(age,brew_where) %>%
  mutate(brew_where = str_trim(brew_where))%>%
  filter(!is.na(brew_where)) %>%
  ggplot(aes(brew_where)) +
  geom_bar(aes(fill = Age)) +
  guides(x = guide_axis(n.dodge=1, angle = 330)) +
  labs(y = "Number of Respondents", title = "Where Coffee is Imbibed")

#WITH TWO EXPANSIONS

coffee_dropped %>%
  #select(submission_id, age, where_drink) %>%
  separate(where_drink, sep=',', fill = 'right', into = c('where1','where2','where3','where4','where5','where6'
                                                   ), remove = TRUE) %>%
  pivot_longer(
    cols = where1:where6,
    names_to = 'list',
    values_to = 'brew_where') %>%
  select(age,brew_where) %>%
  mutate(brew_where = str_trim(brew_where))%>%
  filter(!is.na(brew_where)) %>%
  ggplot(aes(brew_where)) +
  geom_bar(aes(fill = age)) +
  guides(x = guide_axis(n.dodge=1, angle = 330)) +
  labs(y = "Number of Respondents", title = "Where Coffee is Imbibed")


long = coffee_dropped %>%
  #select(submission_id, age, where_drink) %>%
  separate(where_drink, sep=',', fill = 'right', into = c('where1','where2','where3','where4','where5','where6'
                                                   ), remove = TRUE) %>%
  separate(brew, sep=',', fill = 'right', into = c('brew1','brew2','brew3','brew4','brew5','brew6',
                                                   'brew7','brew8','brew9','brew10'), remove = TRUE) %>%
  pivot_longer(
    cols = where1:where6,
    names_to = 'list',
    values_to = 'brew_where') %>%
  pivot_longer(
    cols = brew1:brew10,
    names_to = 'brewct',
    values_to = 'brew_type')

#WORKING 1 expansion
long %>%
  mutate(brew_where = str_trim(brew_where))%>%
  filter(!is.na(brew_where)) %>%
  ggplot(aes(age)) +
  geom_bar(aes(fill = brew_where)) +
  guides(x = guide_axis(n.dodge=1, angle = 330)) +
  labs(y = "Number of Respondents", title = "Where Coffee is Imbibed") +
  annotate("text", x = Inf, y = Inf, label = paste("Total sample size:", 
                                                   sum(!is.na(coffee_dropped$where_drink))), 
           hjust = 1.1, vjust = 2, size = 4, color = "black")

#WORKING 2 expansion
long %>%
  mutate(brew_where = str_trim(brew_where))%>%
  mutate(brew_type = str_trim(brew_type))%>%
  filter((!is.na(brew_where)) & (!is.na(brew_type))) %>%
  ggplot(aes(brew_type)) +
  geom_bar(aes(fill = brew_where)) +
  guides(x = guide_axis(n.dodge=1, angle = 330)) +
  labs(y = "Number of Respondents", title = "Where Coffee is Imbibed") +
  annotate("text", x = Inf, y = Inf, label = paste("Total sample size:", 
                                                   sum(!is.na(coffee_dropped$where_drink))), 
           hjust = 1.1, vjust = 2, size = 4, color = "black")



long %>%
  group_by(submission_id) %>%
  summarise(n()) %>%
  count()

coffee_dropped %>%
  select(Submission_id, Age, Where_drink) %>%
  separate(Where_drink, sep=',', fill = 'right', into = c('where1','where2','where3','where4','where5','where6'
                                                   ), remove = TRUE) %>%
  pivot_longer(
    cols = where1:where6,
    names_to = 'list',
    values_to = 'brew_where') #%>%
  select(Age,brew_where) %>%
  mutate(brew_where = str_trim(brew_where))%>%
  filter(!is.na(brew_where)) %>%
  ggplot(aes(Age)) +
  geom_bar(aes(fill = brew_where)) +
  guides(x = guide_axis(n.dodge=1, angle = 330)) +
  labs(y = "Number of Respondents", title = "Where Coffee is Imbibed")


#Num of respondents
sum(!is.na(coffee_dropped$where_drink))

```
```{r}

coffee_dropped %>%
  select(submission_id, age, where_drink) %>%
  separate(where_drink, sep=',', fill = 'right', 
           into = c('where1','where2','where3','where4','where5','where6'), remove = TRUE) %>%
pivot_longer(
    cols = where1:where6,
    names_to = 'list',
    values_to = 'brew_where') %>%
  select(age,brew_where) %>%
  mutate(brew_where = str_trim(brew_where))%>%
  filter(!is.na(brew_where)) %>%
  ggplot(aes(age)) +
  geom_bar(position = 'fill',aes(fill = brew_where)) +
  guides(x = guide_axis(n.dodge=1, angle = 330)) +
  labs(y = "Number of Respondents", title = "Where Coffee is Imbibed")
```



```{r}
coffee_dropped %>%
  select(submission_id, age, brew, brew_other) %>%
  separate(brew, sep=',', fill = 'right', into = c('brew1','brew2','brew3','brew4','brew5','brew6',
                                                   'brew7','brew8','brew9','brew10'), remove = TRUE) %>%
  pivot_longer(
    cols = brew1:brew10,
    names_to = 'brewct',
    values_to = 'brew_type') %>%
  select(age,brew_type) %>%
  mutate(brew_type = str_trim(brew_type))%>%
  filter(!is.na(brew_type)) %>%
  ggplot(aes(brew_type)) +
  geom_bar(aes(fill = age)) +
  guides(x = guide_axis(n.dodge=1, angle = 330)) +
  labs(x = "Types of Methods", y = "Number of Respondents", title = "Brew Methods")
```
```{r}
coffee_dropped %>%
  select(submission_id, age, purchase) %>%
  separate(purchase, sep=',', fill = 'right', 
           into = c('purchase1','purchase2','purchase3','purchase4','purchase5','purchase6'), remove = TRUE) %>%
  pivot_longer(
    cols = purchase1:purchase6,
    names_to = 'purchasect',
    values_to = 'purchase_type') %>%
  select(age,purchase_type) %>%
  mutate(brew_type = str_trim(purchase_type))%>%
  filter(!is.na(purchase_type)) %>%
  ggplot(aes(purchase_type)) +
  geom_bar(aes(fill = age)) +
  guides(x = guide_axis(n.dodge=1, angle = 330)) +
  labs(y = "Number of Respondents", title = "Purchase Methods")
```
```{r}
coffee_dropped %>%
  select(age,favorite) %>%
  ggplot(aes(favorite)) +
  guides(x = guide_axis(n.dodge=1, angle = 330)) +
  geom_bar(aes(fill = age))

coffee_dropped %>%
  select(age,favorite) %>%
  ggplot(aes(age)) +
  guides(x = guide_axis(n.dodge=1, angle = 330)) +
  geom_bar(position = 'fill', aes(fill = favorite))
```
```{r}
#MILK REVISIT

coffee_dropped %>%
  select(submission_id, age, additions) %>%
  separate(additions, sep='r,', fill = 'right', 
           into = c('additions1','additions2','additions3'), remove = FALSE)
  
  
  
  pivot_longer(
    cols = purchase1:purchase6,
    names_to = 'purchasect',
    values_to = 'purchase_type') %>%
  select(age,purchase_type) %>%
  mutate(brew_type = str_trim(purchase_type))%>%
  filter(!is.na(purchase_type)) %>%
  ggplot(aes(purchase_type)) +
  geom_bar(aes(fill = age)) +
  guides(x = guide_axis(n.dodge=1, angle = 330)) +
  labs(y = "Number of Respondents", title = "Purchase Methods")
```
```{r}
yes_tasting %>%
  select(submission_id, coffee_a_acidity, coffee_a_bitterness, coffee_a_personal_preference,
         coffee_b_acidity, coffee_b_bitterness, coffee_b_personal_preference,
         coffee_c_acidity, coffee_c_bitterness, coffee_c_personal_preference,
         coffee_d_acidity, coffee_d_bitterness, coffee_d_personal_preference) %>%
  mutate(across(1:12, as.numeric))
```


```{r}
#COFFEE A

#Density Plot
yes_tasting %>%
  select(coffee_a_acidity, coffee_a_bitterness, coffee_a_personal_preference) %>%
  mutate(across(1:3, as.numeric)) %>%
  pivot_longer(cols = starts_with('coffee'), names_to = 'Characteristic', values_to = 'Rating') %>%
  ggplot(aes(x = Rating)) +
  geom_density(aes(Rating, color = Characteristic), binwidth = 1, adjust = 4)

#Dot Plot
yes_tasting %>%
  select(coffee_a_acidity, coffee_a_bitterness, coffee_a_personal_preference, coffee_a_notes) %>%
  ggplot(aes(coffee_a_acidity,coffee_a_bitterness)) +
  geom_count() +
  labs(x = "Acidity", y = "Bitterness", title = "Coffee A Metrics")

#Contour Plot
yes_tasting %>%
  select(coffee_a_acidity, coffee_a_bitterness, coffee_a_personal_preference, coffee_a_notes) %>%
  ggplot(aes(coffee_a_acidity,coffee_a_bitterness)) +
  geom_contour_filled(aes(z = coffee_a_personal_preference)) +
  labs(x = "Acidity", y = "Bitterness", z = "Preference Rating", title = "Coffee A Metrics")

#class(yes_tasting$coffee_a_acidity[1])
```
```{r}





#HMMM
geom_density(aes(coffee_a_bitterness, color = 'darkgoldenrod'), binwidth = 1, adjust = 4) +
  geom_density(aes(coffee_a_personal_preference, color = 'aquamarine3'), binwidth = 1, adjust = 4) +
  geom_density(aes(coffee_a_acidity, color = 'red'), kernel = "gaussian") +
  geom_density(aes(coffee_a_bitterness, color = 'blue')) +
  geom_density(aes(coffee_a_personal_preference))
```

```{r}

#B Word Cloud

yes_tasting$coffee_a_notes = gsub("\\p{P}",'',yes_tasting$coffee_a_notes, perl = TRUE)
yes_tasting$coffee_a_notes = tolower(yes_tasting$coffee_a_notes)


head(yes_tasting,100) %>%
  select(submission_id, coffee_a_notes) %>%
  filter(!is.na(coffee_a_notes)) %>%
  separate_wider_delim(col = coffee_a_notes, delim = " ",
                       names = c("var1", "var2", "var3", "var4", "var5", "var6", "var7", "var8", "var9", "var10", "var11", "var12", "var13", "var14", "var15", "var16"),  
                       too_many = "debug",
                       too_few = "debug") %>%
  pivot_longer(cols = starts_with('var'),
               names_to = 'place',
               values_to = 'words', 
               values_drop_na = TRUE) %>%
  mutate(words = str_trim(words)) %>%
  count(words, name = 'count') %>%
  filter(words %in% c("a", "i", "4", "3rd", "bit", "and", "it", "b") == FALSE) %>%
  ggplot(aes(label = words, size = count, color = count)) +
  geom_text_wordcloud_area(rm_outside = TRUE, eccentricity = 1) +
  scale_size_area(max_size = 50, trans = power_trans(1/.7)) +
  theme_minimal() +
  scale_color_gradient(low = "darkred", high = "red")

```
```{r}
head(yes_tasting,1000) %>%
  select(submission_id, coffee_a_notes) %>%
  filter(!is.na(coffee_a_notes)) %>%
  mutate(coffee_a_notes = str_replace_all(coffee_a_notes, "[<>.*]", " ")) #%>%
  separate_wider_delim(col = coffee_a_notes, delim = " ",
                       names = c("var1", "var2", "var3", "var4", "var5", "var6", "var7", "var8", "var9", "var10", "var11", "var12", "var13", "var14", "var15", "var16"),  
                       too_many = "debug",
                       too_few = "debug") 

head(yes_tasting,1000) %>%
  select(submission_id, coffee_a_notes) %>%
  filter(!is.na(coffee_a_notes)) %>%
  separate_wider_regex(col = coffee_a_notes, 
                       c(var1 = ".*?", "_", var2 = ".*"),
                       too_few = "debug")
                       
```


```{r}
#A Test passed
#B Test passed
#C Test passed
#D Test passed
coffee_cleaning %>%
  select(submission_id, coffee_d_notes) %>%
  filter(!is.na(coffee_d_notes)) %>%
  mutate(coffee_d_notes = str_replace_all(coffee_d_notes, "[<>.*]", " ")) %>%
  separate_wider_delim(col = coffee_d_notes, delim = " ",
                       names = c("var1", "var2", "var3", "var4", "var5", "var6", "var7", "var8", "var9", "var10", "var11", "var12", "var13", "var14", "var15", "var16"),  
                       too_many = "debug",
                       too_few = "debug") %>%
  pivot_longer(cols = starts_with('var'),
               names_to = 'place',
               values_to = 'words', 
               values_drop_na = TRUE) %>%
  mutate(words = str_trim(words)) %>%
  mutate(words = str_replace(words, ",", "")) %>%
  mutate(words = tolower(words)) %>%
  count(words, name = 'count') %>%
  filter((count > 5) & (count < 100)) %>%
  filter(words %in% c("as","a", "i", "4", "3rd", "bit", "and", "it", "b", "<ul>", "&","-") == FALSE) %>%
  ggplot(aes(label = words, size = count, color = count)) +
  geom_text_wordcloud_area(rm_outside = TRUE, eccentricity = 1) +
  scale_size_area(max_size = 50, trans = power_trans(1/.7)) +
  theme_minimal() +
  scale_color_gradient(low = "darkred", high = "red")

```
```{r}


```

```{r}
#COFFEE B

#Dot Plot
yes_tasting %>%
  select(coffee_b_acidity, coffee_b_bitterness, coffee_b_personal_preference, coffee_b_notes) %>%
  ggplot(aes(coffee_b_acidity,coffee_b_bitterness)) +
  geom_count() +
  labs(x = "Acidity", y = "Bitterness", title = "Coffee B Metrics")

#Contour Plot
yes_tasting %>%
  select(coffee_b_acidity, coffee_b_bitterness, coffee_b_personal_preference, coffee_b_notes) %>%
  ggplot(aes(coffee_b_acidity,coffee_b_bitterness)) +
  geom_contour_filled(aes(z = coffee_b_personal_preference)) +
  labs(x = "Acidity", y = "Bitterness", z = "Preference Rating", title = "Coffee B Metrics")

  #Density Plot
yes_tasting %>%
  select(coffee_b_acidity, coffee_b_bitterness, coffee_b_personal_preference) %>%
  mutate(across(1:3, as.numeric)) %>%
  pivot_longer(cols = starts_with('coffee'), names_to = 'Characteristic', values_to = 'Rating') %>%
  ggplot(aes(x = Rating)) +
  geom_density(aes(Rating, color = Characteristic), binwidth = 1, adjust = 4)
```
```{r}

#B Word Cloud

yes_tasting$coffee_b_notes = gsub("\\p{P}",'',yes_tasting$coffee_b_notes, perl = TRUE)
yes_tasting$coffee_b_notes = tolower(yes_tasting$coffee_b_notes)


head(yes_tasting,100) %>%
  select(submission_id, coffee_b_notes) %>%
  filter(!is.na(coffee_b_notes)) %>%
  separate_wider_delim(col = coffee_b_notes, delim = " ",
                       names = c("var1", "var2", "var3", "var4", "var5", "var6", "var7", "var8", "var9", "var10", "var11", "var12", "var13", "var14", "var15", "var16"),  
                       too_many = "debug",
                       too_few = "debug") %>%
  pivot_longer(cols = starts_with('var'),
               names_to = 'place',
               values_to = 'words', 
               values_drop_na = TRUE) %>%
  mutate(words = str_trim(words)) %>%
  count(words, name = 'count') %>%
  filter(words %in% c("a", "i", "4", "3rd", "but", "it", "b") == FALSE) %>%
  ggplot(aes(label = words, size = count, color = count)) +
  geom_text_wordcloud_area(rm_outside = TRUE, eccentricity = 1) +
  scale_size_area(max_size = 50, trans = power_trans(1/.7)) +
  theme_minimal() +
  scale_color_gradient(low = "brown", high = "black")


```


```{r}
#COFFEE C

#Dot Plot
yes_tasting %>%
  select(coffee_c_acidity, coffee_c_bitterness, coffee_c_personal_preference, coffee_c_notes) %>%
  ggplot(aes(coffee_c_acidity,coffee_c_bitterness)) +
  geom_count() +
  labs(x = "Acidity", y = "Bitterness", title = "Coffee C Metrics")

#Countour Plot
yes_tasting %>%
  select(coffee_c_acidity, coffee_c_bitterness, coffee_c_personal_preference, coffee_c_notes) %>%
  ggplot(aes(coffee_c_acidity,coffee_c_bitterness)) +
  geom_contour_filled(aes(z = coffee_c_personal_preference)) +
  labs(x = "Acidity", y = "Bitterness", z = "Preference Rating", title = "Coffee C Metrics")

#Density Plot
yes_tasting %>%
  select(coffee_c_acidity, coffee_c_bitterness, coffee_c_personal_preference) %>%
  mutate(across(1:3, as.numeric)) %>%
  pivot_longer(cols = starts_with('coffee'), names_to = 'Characteristic', values_to = 'Rating') %>%
  ggplot(aes(x = Rating)) +
  geom_density(aes(Rating, color = Characteristic), binwidth = 1, adjust = 4)
```
```{r}

#C Word Cloud 
yes_tasting$coffee_c_notes = gsub("\\p{P}",'',yes_tasting$coffee_c_notes, perl = TRUE)
yes_tasting$coffee_c_notes = tolower(yes_tasting$coffee_c_notes)


head(yes_tasting,100) %>%
  select(submission_id, coffee_c_notes) %>%
  filter(!is.na(coffee_c_notes)) %>%
  separate_wider_delim(col = coffee_c_notes, delim = " ",
                       names = c("var1", "var2", "var3", "var4", "var5", "var6", "var7", "var8", "var9", "var10", "var11", "var12", "var13", "var14", "var15", "var16"),  
                       too_many = "debug",
                       too_few = "debug") %>%
  pivot_longer(cols = starts_with('var'),
               names_to = 'place',
               values_to = 'words', 
               values_drop_na = TRUE) %>%
  mutate(words = str_trim(words)) %>%
  count(words, name = 'count') %>%
  filter(words %in% c("a", "i", "b", "c", "but") == FALSE) %>%
  ggplot(aes(label = words, size = count, color = count)) +
  geom_text_wordcloud_area(rm_outside = TRUE, eccentricity = 1) +
  scale_size_area(max_size = 50, trans = power_trans(1/.7)) +
  theme_minimal() +
  scale_color_gradient(low = "chocolate", high = "chocolate4")
```


```{r}
#COFFEE D

#Dot Plot
yes_tasting %>%
  select(coffee_d_acidity, coffee_d_bitterness, coffee_d_personal_preference, coffee_d_notes) %>%
  ggplot(aes(coffee_d_acidity,coffee_d_bitterness)) +
  geom_count() +
  labs(x = "Acidity", y = "Bitterness", title = "Coffee D Metrics")

#Contour Plot
yes_tasting %>%
  select(coffee_d_acidity, coffee_d_bitterness, coffee_d_personal_preference, coffee_d_notes) %>%
  ggplot(aes(coffee_d_acidity,coffee_d_bitterness)) +
  geom_contour_filled(aes(z = coffee_d_personal_preference)) +
  labs(x = "Acidity", y = "Bitterness", z = "Preference Rating", title = "Coffee D Metrics")

yes_tasting %>%
  select(coffee_d_acidity, coffee_d_bitterness, coffee_d_personal_preference, coffee_d_notes) %>%
  ggplot(aes(coffee_d_acidity,coffee_d_bitterness)) + 
  geom_density_2d() + 
  geom_point()

#Density Plot
yes_tasting %>%
  select(coffee_d_acidity, coffee_d_bitterness, coffee_d_personal_preference) %>%
  mutate(across(1:3, as.numeric)) %>%
  pivot_longer(cols = starts_with('coffee'), names_to = 'Characteristic', values_to = 'Rating') %>%
  ggplot(aes(x = Rating)) +
  geom_density(aes(Rating, color = Characteristic), binwidth = 1, adjust = 4)
```
```{r}
yes_tasting$coffee_d_notes = gsub("\\p{P}",'',yes_tasting$coffee_d_notes, perl = TRUE)
yes_tasting$coffee_d_notes = tolower(yes_tasting$coffee_d_notes)


head(yes_tasting,100) %>%
  select(submission_id, coffee_d_notes) %>%
  filter(!is.na(coffee_d_notes)) %>%
  separate_wider_delim(col = coffee_d_notes, delim = " ",
                       names = c("var1", "var2", "var3", "var4", "var5", "var6", "var7", "var8", "var9", "var10", "var11", "var12", "var13", "var14", "var15", "var16"),  
                       too_many = "debug",
                       too_few = "debug") %>%
  pivot_longer(cols = starts_with('var'),
               names_to = 'place',
               values_to = 'words', 
               values_drop_na = TRUE) %>%
  mutate(words = str_trim(words)) %>%
  count(words, name = 'count') %>%
  filter(words %in% c("a", "and", "i", "4", "3rd", "but", "it", "b") == FALSE) %>%
  ggplot(aes(label = words, size = count, color = count)) +
  geom_text_wordcloud_area(rm_outside = TRUE, eccentricity = 1) +
  scale_size_area(max_size = 50, trans = power_trans(1/.7)) +
  theme_minimal() +
  scale_color_gradient(low = "darkorange2", high = "darkorange")
```
```{r}
#Facets

#Define Master Metrics
metrics = rbind(
yes_tasting %>%
  select(submission_id, coffee_a_acidity, coffee_a_bitterness, coffee_a_personal_preference) %>%
  rename(acidity = coffee_a_acidity, bitterness = coffee_a_bitterness, personal = coffee_a_personal_preference ) %>%
  mutate(type = 'A'),
yes_tasting %>%
  select(submission_id, coffee_b_acidity, coffee_b_bitterness, coffee_b_personal_preference) %>%
  rename(acidity = coffee_b_acidity, bitterness = coffee_b_bitterness, personal = coffee_b_personal_preference ) %>%
  mutate(type = 'B'),
yes_tasting %>%
  select(submission_id, coffee_c_acidity, coffee_c_bitterness, coffee_c_personal_preference) %>%
  rename(acidity = coffee_c_acidity, bitterness = coffee_c_bitterness, personal = coffee_c_personal_preference ) %>%
  mutate(type = 'C'),
yes_tasting %>%
  select(submission_id, coffee_d_acidity, coffee_d_bitterness, coffee_d_personal_preference) %>%
  rename(acidity = coffee_d_acidity, bitterness = coffee_d_bitterness, personal = coffee_d_personal_preference ) %>%
  mutate(type = 'D'), deparse.level = 1
) %>%
  mutate(type = as.factor(type))

#Count Plot
metrics %>%
  ggplot(aes(x = acidity)) +
  geom_count(aes(x = acidity, y = bitterness)) +
  facet_wrap(. ~ type) +
  labs(x = "Acidity", y = "Bitterness", title = "Bitterness v Acidity")

# 2D Density
metrics %>%
  ggplot(aes(x = acidity, y = bitterness)) +
  geom_density_2d() + 
  geom_point() +
  facet_wrap(. ~ type)

#Countour Plot
metrics %>%
  ggplot(aes(x = acidity, y = bitterness)) +
  geom_contour_filled(aes(z = personal)) +
  facet_wrap(. ~ type) +
  labs(x = "Acidity", y = "Bitterness", z = "Preference Rating", title = "Bitterness, Acidity, Preference")

#Density Plot
metrics %>%
  ggplot(aes(x = personal)) +
  geom_density(aes(personal, color = 'personal'), binwidth = 1, adjust = 4) +
  geom_density(aes(acidity, color = 'acidity'), binwidth = 1, adjust = 4) +
  geom_density(aes(bitterness,color = 'bitterness'), binwidth = 1, adjust = 4) +
  facet_wrap(. ~ type)

metrics
```




```{r}
#Preference
yes_tasting %>%
  ggplot(aes(prefer_abc)) +
  geom_bar() +
  labs(x = "Peferred Type", y = "Number of Respondents", title = "Preference: A vs. B vs. C", )
```

```{r}
preferences = yes_tasting %>%
  select(coffee_a_personal_preference, coffee_b_personal_preference, 
         coffee_c_personal_preference, coffee_d_personal_preference) %>%
  rename('Coffee A' = coffee_a_personal_preference, 'Coffee B' = coffee_b_personal_preference,
         'Coffee C' = coffee_c_personal_preference, 'Coffee D' = coffee_d_personal_preference) %>%
  pivot_longer(cols = starts_with('Coffee'), 
               names_to = 'CoffeeType', 
               values_to = 'PreferenceRating') 

preferences$CoffeeType = as.factor(preferences$CoffeeType)
preferences$PreferenceRating = preferences$PreferenceRating*1.0

preferences %>%
  filter(!is.na(preferences$PreferenceRating)) %>%
  group_by(CoffeeType) %>%
  summarise(mean(PreferenceRating), n()) 

preferences %>%
  filter(!is.na(preferences$PreferenceRating)) %>%
  ggplot(aes(x=CoffeeType, y=PreferenceRating, color = CoffeeType)) +
  geom_violin( bw = .4) + stat_summary(fun.y=mean, geom="point", shape=23, size=2, color = 'brown') +
  geom_boxplot(aes(middle = mean(PreferenceRating)), width = .08) +
  geom_boxplot(fatten = NULL, width = .08) +
  stat_summary(fun.y = mean, geom = "errorbar", aes(ymax = ..y.., ymin = ..y..),
               width = 0.08, size = 1, linetype = "solid") +
  labs(title = "Preference Rating Distribution")

```

```{r}
# Testing if there is difference between B and C 2 Sample T Test and F Test

#Except NULL for F Test, variances are similiar
var.test(coffee_dropped$coffee_b_personal_preference, coffee_dropped$coffee_c_personal_preference, alternative = "two.sided")[3] #p = 0.4149961

#Except NULL for T Test, no difference between means
t.test(coffee_dropped$coffee_b_personal_preference, coffee_dropped$coffee_c_personal_preference, alternative = "two.sided")[3] #p = 0.8813144

#ALL other comparisons failed the F Test
var.test(coffee_dropped$coffee_d_personal_preference, coffee_dropped$coffee_a_personal_preference, alternative = "two.sided")[3] 

#All other comparisons reject NULL for T Test
t.test(coffee_dropped$coffee_d_personal_preference, coffee_dropped$coffee_a_personal_preference, alternative = "two.sided")[3] 

```

```{r}

```


Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Cmd+Option+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Cmd+Shift+K* to preview the HTML file). 

The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.

